Viscous Erosion in Porous Media

### 2018-03-26 docs/methods/erosion_methods.tex
NM

	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process. Notice the body obtains a similar profile as observed previously, but with fixed area. Importantly, more numerical accuracy is now available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) is a zoom showing that, due to our numerical regularization, the near corner at the body's rear is actually smooth on a fine scale. We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces. As observed before, the stress becomes more evenly distributed as erosion reshapes the body. The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy. Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points. In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/arangle.pdf}
\caption{Shape characteristics of an eroding body: (a) The aspect ratio, defined as the width to height, versus time. (b) The measured opening angle versus time. For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024. In the most resolved simulation (5/1024) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$ in long time.}
\label{fig:arangle}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state. In particular, we measure the aspect ratio of the body (the ratio of width to height) and the opening angle of the front/rear corner. As shown in Fig.~\ref{fig:arangle}(a)

>>>>

	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before. Notice the body obtains a similar profile as observed previously, but with fixed area. Importantly, more numerical accuracy is now available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) is a zoom showing that, due to our numerical regularization, the near corner at the body's rear is actually smooth on a fine scale. We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces. As observed before, the stress becomes more evenly distributed as erosion reshapes the body. The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy. Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points. In this figure, time is normalized by the same value $t_f = 1.79 \times 10^{-2}$ as in Fig.~\ref{shrink_intface}.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/arangle.pdf}
\caption{Shape characteristics of an eroding body: (a) The aspect ratio (width to height) versus time. (b) The measured opening angle versus time. For both measurements, we show three cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024. In the finest simulation ($5/1024$) the aspect ratio converges to 2.7 and the opening angle converges to the predicted value of $102^{\circ}$ in long time.}
\label{fig:arangle}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024c5
% Uses 01circ1024.in with epsfac = 5, sigfac = 5, dt = 2e-4, fixarea = 1, fixpdrop = 0

These fixed-area simulations enable us to precisely characterize the changing geometry as it approaches a terminal state. In particular, we measure the aspect ratio of the body (the width to height) and the opening angle of the front/rear corner as they vary in time. In these tests, we keep the spatial resolution fixed, $N_\iin = 1024$, and show three different cases of the smoothing parameters: $\eps = \sigma = 20/1024, 10/1024,$ and 5/1024.
